### 2016-10-07 paper/intro_v2.tex
New branch created for intro, modified intro in paper/intro_v2.tex

\section{Introduction}

In scientific and engineering contexts, physical systems are represented by mathematical models, which often take the form of partial differential equations (PDEs). These models are characterized by a set of parameters, and relate these parameters to states that can be observed. In the inverse problem, the parameters are unknown and one tries to infer their values based on observations of the states or parameters \cite{Taran05, BanksKuhn89}. For a range of applications, the parameters may be numerous, and yet what is ultimately of interest may be some low-dimensional Quantity of Interest (QoI); we refer to the setting where the goal of inferring parameters is to use them in predicting a QoI as a \textit{goal-oriented inverse problem}. A given physical system can be represented with varying degrees of fidelity by different models; a higher-fidelity model is able to more accurately represent reality, but is also usually more difficult to solve. In the context of the goal-oriented inverse problem, one may choose a lower-fidelity model with which to perform inference, sacrificing accuracy in the state and/or parameters in exchange for reduced computational costs while keeping the error in the QoI to within some acceptable tolerance. In this work, we present an approach to manage the fidelity of modeling choices in solving the inverse problem, so as to achieve a desired level of accuracy in the QoI prediction, without necessarily resolving the parameters accurately. We adaptively form a mixed-fidelity model with which we solve the inverse problem by using models of different levels of fidelity in different parts of the domain.

@@

We aim to combine the ideas in goal-oriented methods for inverse problems, and goal-oriented model adaptivity approaches for forward modeling. The objective of this work is to formulate a method that allows one to systematically manage the use of multiple models in the context of the goal-oriented inverse problem, so as to minimize the error in a QoI prediction. To do this, we first assume that solving the inverse problem with the highest-fidelity model would result in the most accurate QoI, but that solving this inverse problem is prohibitively expensive. We derive a third-order estimate for the QoI error from inferring the parameters using a lower-fidelity model. This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI.

>>>>

\section{Introduction}
%
Physical and engineering systems are often described using sophisticated mathematical models, such as coupled, nonlinear partial differential equations. Recent years have seen important advances in the accurate and reliable solution of the `forward problem', i.e.\ the solution of such complex models given appropriate initial/boundary conditions and constitutive parameters. In particular, adaptive methods have emerged as a highly effective paradigm for solving the forward problem. `Goal-oriented error estimation' algorithms are an important subset of adaptive methods, where a computational grid or even the model itself is adapted to obtain the desired accuracy in a particular goal (QoI), while minimizing the number of grid points or model complexity.

Often, the solution of the forward problem is embedded in a larger framework, where our objective is to either infer unknown model parameters (inverse problems) or the selection of optimal parameters to minimize or maximize a desired quantity (optimization problems) \cite{Taran05, BanksKuhn89}. Such inverse problems present a computational major challenge, since they often involve repeated solutions of the forward problem, and contain additional equations that arise from their mathematical formulation. Adaptive methods have been applied to make inverse problems tractable as well, including work on the \textit{goal-oriented inverse problem}. In a goal-oriented inverse problem, the emphasis is on identifying a low dimensional subset of the parameter or state space, which is both informed by the data, and has an impact on the goal functional. Various algorithms have been presented in the literature for solving the goal-oriented inverse problem, however, there has been little work in the use of adaptive modeling in such a setting.

In this work, we present a robust, adaptive framework for the solution of goal-oriented inverse problems, which can identify the appropriate subset of the parameter, state space or model features/complexity to achieve a desired accuracy in the QoI. In doing so, we aim to combine the ideas from goal-oriented model adaptivity for forward problems, and goal-oriented methods for inverse problems. In particular, our method that allows one to systematically manage the use of multiple models, in an inverse problem, so as to minimize the error in a QoI prediction. Taking the inverse problem with the highest-fidelity model as our reference QoI prediction, we derive a third-order estimate for the QoI error from using a lower-fidelity model. This estimate can be localized, and the error decomposition then used to guide the formation of mixed-fidelity models with which to solve the inverse problem, while minimizing the error in the QoI.

@@
